Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2024-09-04 reviews.Rmd
adjust intro to letter

---
title          : "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization"
authors        : "Aaron Peikert, Maximilian S. Ernst & Andreas M. Brandmaier"
journal        : "Meta-Psychology"
manuscript-id  : "4139"
manuscript-src : "headings"
bibliography   : references.bib
cutout-quotes  : true
class          : "draft"
output         : papaja::revision_letter_pdf
---

@@

thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_.
In the following we address your and each reviewers'/editors' concerns point-by-point.
For Daniel Laken's review we took the liberty to additionally include a high level summary, since we found it, at times, hard to follow the different interwoven discussions.

@@

@@

Control vs Transparency:

@@

* Reviewer Concern: The terminology used, particularly “theoretical risk,” was seen as potentially confusing and misaligned with existing literature, such as the concept of severity.
* Our Response: We provided additional references and explanations to support our terminology. We believe our terms accurately reflect the concepts within our Bayesian framework, but we differentiated our terminology further from frequentist reasoning.

@@

:::reviewer
\label{pt:harking}
Conclusion: Again, I appreciate the authors digging in to the justification of preregistration, but I think there are some important things missing in this version of the manuscript.
How can the article be improved? The authors should address harking.
:::

@@

:::reviewer
\label{pt:nullhacking}
They should also address 'null-hacking'.
:::

>>>>

---
title          : "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization"
authors        : "Aaron Peikert, Maximilian S. Ernst & Andreas M. Brandmaier"
journal        : "Meta-Psychology"
manuscript-id  : "4139"
cutout-quotes  : true
class          : "draft"
output         : papaja::revision_letter_pdf
manuscript-src : manuscript.Rmd
---

@@

thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_.
In the following we address your and each reviewers'/editors' concerns point-by-point.

@@

For Daniel Laken's review we took the liberty to additionally include a high level summary, since we found it, at times, hard to follow the different interwoven discussions.
We took special care to change the manuscript in response to his summary of suggestions (RC \@ref(pt:change-start) to RC \@ref(pt:change-end)).

Due to a technical issue, the citations in the manuscript excerpts in this letter do not work correctly (they are correct in the manuscript, however).

@@

Control vs. Transparency:

@@

* Reviewer Concern: The terminology used, particularly "theoretical risk," was seen as potentially confusing and misaligned with existing literature, such as the concept of severity.
* Our Response: We provided additional references and explanations to support our terminology. We believe our terms accurately reflect the concepts within our Bayesian framework, but we differentiated our terminology further from frequentist reasoning.

@@

:::reviewer
\label{pt:change-start}

\label{pt:harking}
Conclusion: Again, I appreciate the authors digging in to the justification of preregistration, but I think there are some important things missing in this version of the manuscript.
How can the article be improved? The authors should address harking.
:::

@@

:::reviewer
\label{pt:change-end}
\label{pt:nullhacking}
They should also address 'null-hacking'.
:::
